Response to Pachter’s Review

### 2020-01-22 index.Rmd
modified graphic

#perform test 1000 times
Dist <- matrix(0,nrow=1,ncol=1000)
for (i in 1:1000){
  Dist[,i]<-ageMatchedRandom()
}
hist(Dist, main="Age Matched Test Google Scholar Citations without Lior Pachter ")
```

@@

plot(x.age.range,x.c,
  type="l",
  col="chartreuse3",
  ylim=c(0,7000),
  main="Average citations of Professors beneath specified years since PhD \n (Lior Pachter removed)",
  ylab="mean citations",
  xlab="PhD age",
  lwd=2)
lines(x.age.range,x.a,
  type="l",
  col="red",
  lwd=2)
legend("topleft",
  c("Letter A","Letter C"),
  fill=c("red","chartreuse3"))

>>>>

#perform test 1000 times
Dist <- matrix(0,nrow=1,ncol=1000)
for (i in 1:1000){
  Dist[,i]<-ageMatchedRandom()
}
hist(Dist, main="Age Matched Test Google Scholar Citations \n without Lior Pachter ")
```

@@

plot(x.age.range,x.c,
  type="l",
  col="chartreuse3",
  ylim=c(0,7000),
  main="Average citations of Professors as a function of PhD Age \n (Lior Pachter removed)",
  ylab="mean citations",
  xlab="PhD age",
  lwd=2)
lines(x.age.range,x.a,
  type="l",
  col="red",
  lwd=2)
legend("topleft",
  c("Letter A","Letter C"),
  fill=c("red","chartreuse3"))
